Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-17 Submission.tex
revisiting n's

Prior to considering the subsequent empirical work done on this topic, it is of value to explore \emph{why} there is expected to be different outcomes associated with these forms of demands. M. A. LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes. Similar to the job-demands resources theory (Bakker \& Demerouti, 2017), challenge and hindrance demands elicit two different paths or processes. First, challenge stressors typically result in a challenge appraisal, and both engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. The other side of the coin is that this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions (M. A. LePine, 2022).

@@

Having evidence that people can make a distinction between challenge and hindrance stressors, the next logical question is whether they do relate differentially to outcomes. The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. For example, Cavanaugh et al. (2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. Chen et al. (2021) found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it (Crawford et al., 2010). Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009). Lastly, Gerich (2017) concluded that employee well-being was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

@@

Horan et al. (2020) and M. A. LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). In fact, Horan et al. (2020) suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons. Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015). TRANSITION?

@@

\#\#Current Study and Hypotheses

@@

>>>>

Prior to considering the subsequent empirical work done on this topic, it is of value to explore \emph{why} there is expected to be different outcomes associated with these forms of demands. M. A. LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes. Similar to the job-demands resources theory (Bakker \& Demerouti, 2017), challenge and hindrance demands elicit two different paths or processes. First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. The other side of the coin is that this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions (M. A. LePine, 2022).

@@

Having evidence that people can make a distinction between challenge and hindrance stressors, the next logical question is whether they do relate differentially to outcomes. The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. For example, Cavanaugh et al. (2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. Chen et al. (2021) found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it (Crawford et al., 2010). Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009). Lastly, Gerich (2017) concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

@@

Horan et al. (2020) and M. A. LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). In fact, Horan et al. (2020) suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons. Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015). THE TRANSITION NEEDED HERE COULD ADDRESS RENATA'S RECOMMENDATION TO TIE THIS LITERATURE BACK INTO THE JOB-DEMANDS RESOURCES MODEL.

@@

\hypertarget{current-study-and-hypotheses}{%
\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}

@@

\begin{verbatim}
##         V1 V2 V3 V4 V5 V6 V7 V8 V9 V10 V11 V12 V13 V14 V15 V16 V17 V18 V19 V20
## item118  3  5  4  1  5  4  3  4  5   4   2   5   4  NA   2   5   5   4   4   5
## item119  4  5  4  3  5  2  3  5  5  NA  NA   2  NA  NA  NA   5   5   4  NA  NA
## item120  2  4  5  4  5  2  2  5  4   4   3   3   4   5   1   5   5   3  NA   5
## item121  4  5  5  2  5  5  4  4  5   4   4   3   4   5   4   3   5   4   5   3
## item122 NA  4 NA  4  3 NA NA  1  2   2   3   3  NA   3   4  NA   5  NA   4  NA
## item123  4  4  3 NA NA  4 NA  2  5   3   4   3   2   4  NA  NA   1   4   2  NA
## item124  4  5  4  4  2  4  3  2  5   2   5   5   3   2   3   5   1   4   2   1
## item125  4  2  3 NA  2 NA NA  2  1   4   4   3   2   3   4   1   4  NA  NA   5
## item126  3  4  2  3  5  5  2  3  4  NA   4   2  NA   5   2   1   5   3   5  NA
## item127  3  4  3  4  2  5  2  3  4   4   4   1   5   5   2   1   5   4   4   4
## item128  1 NA NA NA NA NA NA NA  2  NA  NA  NA  NA  NA   1  NA   4  NA  NA  NA
## item129  4 NA NA  4 NA NA NA NA NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA
## item130 NA NA NA NA NA NA NA NA NA   1  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA
## item131  2  4  3  2  3  4  3  4  5   5   4  NA   5   4   5   3   5  NA  NA  NA
## item132  4  2 NA NA NA NA NA  4 NA  NA   2  NA  NA  NA   1  NA  NA  NA   4   4
## item133  3  1 NA NA NA NA NA NA NA   1  NA  NA   2  NA   3  NA  NA  NA  NA   1
## item134 NA NA NA NA NA NA NA NA NA   4  NA   3   4  NA   4  NA  NA  NA  NA   1
## item135  4  4  2  4  3  2  5  4  5   4   2   4   3   4   3   3   4   3   4   1
## item136 NA NA NA NA NA NA NA  2  2   1   2   2   2  NA   2  NA  NA  NA  NA  NA
## item137 NA  2 NA  4 NA NA NA NA  1   3   3  NA   2  NA   4  NA   4  NA  NA  NA
## item138 NA  3 NA NA NA NA NA NA NA   4   4  NA   2  NA  NA  NA   4  NA  NA  NA
## item139 NA  2 NA NA NA NA NA NA  4   3  NA   1   2  NA   2  NA   2  NA  NA  NA
## item140  4  3 NA NA NA  3  2 NA  4   3  NA  NA   3  NA   4  NA   4  NA  NA   1
## item141  3 NA  2  3  3  4  4  2 NA   5   3   3   4   2   4   3   1   2   4   1
## item142  2  2 NA  4 NA  4 NA  4  3   4   3   3   5  NA   4   3   4  NA   3   1
## item143  2  3 NA  3 NA NA  2 NA  1   4   4   3   4  NA   5   3   5  NA   3   1
## item144  2  3 NA NA NA  4 NA  4  4   3  NA  NA   5  NA   5  NA   4   2   1   1
## item146 NA NA NA NA NA NA NA NA NA   1   3  NA   1  NA   2  NA  NA  NA  NA   1
## item147 NA NA NA NA NA NA NA  5 NA   5  NA  NA  NA   4  NA  NA  NA  NA  NA   4
## item148 NA NA NA NA NA NA NA  5 NA   5  NA  NA  NA  NA  NA  NA   5  NA  NA   3
## item149  2  4  4  3  3  5  2  4  5  NA   2   5   3   5   5   5   5   4   4   5
## item150  3  4  4  3  5  4 NA  4  2   5   4   5   4   5   4   5   5   4   3   4
## item151  2  4  3  2  3 NA  4  3  5   3   4   4   4   3  NA   4   5   4   5   5
## item152  3  3 NA  4  3  4 NA  2  5  NA   1   2   1  NA  NA   4   1   4   5   5
## item153  5  5  3  1  5  4  5  4 NA  NA   3   4  NA   5  NA   3   4   3   5  NA
## item154  3  5  3  5  5  5  4  5  3   4   4   5   4   4   4   4   5   4   5   5
## item155  1  3  3  4  4  4  2  3  2  NA   2   4   2   3   2   4   4   3   4   5
## item156  3  4 NA  3  5  4 NA  3 NA  NA   3   2  NA  NA   4   4   5   4   5  NA
## item157  3  4  4  1 NA  5 NA  5  4  NA   4   5  NA   5  NA   4   5   4  NA  NA
## item158  2  4  4  3  5  4 NA  4  4   4   3   4   4  NA  NA   4   4   4   2   4
## item159  2  3 NA  4  3 NA NA  5  3   4   3   3   3  NA   1   4   5   4   2   5
## item160  4  5 NA  3  5  4  1  5  2  NA   4   3   5   4  NA   3   2   3   4  NA
## item161 NA NA NA NA NA  5 NA NA NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA
## item162  3  4 NA NA NA NA  1  5  5   2   5  NA   4   4   5  NA   4   4   2   3
## item163  3  4  4  1  5  5  2  5  3   4   5   3   4   4   2   4   4   4   5   3
## item164  4  4  4  5  5 NA  3  4  5   3   5  NA  NA  NA   3   3   4   4   5   4
## item165  3  3 NA  3 NA NA NA  4  5   2  NA  NA  NA  NA   5  NA   4  NA  NA  NA
## item166  4  4  4  2  5 NA NA  4  2   3  NA  NA  NA  NA   4  NA   4  NA  NA  NA
## item167  3  4  4 NA  5  5  4  4 NA  NA   4   3  NA  NA  NA   5   5   4   5  NA
## item168  2  4  4  4  5  5 NA  5  5  NA   4   5  NA   5   3   5   5   5   4  NA
## item169  3  3  3  3  5  5  2  5  2   4  NA   5   2  NA  NA   5   4   4   4   3
## item170  4  4  5  4  5 NA NA  5  5  NA  NA   5   5  NA  NA   5   5   3  NA  NA
## item171  4  5  4  3  5  5  1  4  3  NA   4   5  NA   5   5   5   5   4   5  NA
## item172  3  5  4  4  5  5  2  5  4   5   4   5   5   5  NA   4   5   4   5   3
## item173  4  4  3  5  3  5  4  4  4  NA   5   4  NA   4   2   3   4   3   3   1
## item174  3  4  4  1  5  4 NA  4 NA  NA   5   5   4  NA  NA   3   4   3   2  NA
## item175  2  3  4  4  5 NA  5  4 NA   3   5   4  NA  NA  NA   4   4   5   3  NA
## item176  4  5  4  2  5  4  3  4  2   4   5   5  NA   5  NA   5   5   4   4   4
## item177  5 NA NA NA NA NA NA NA  1   4  NA  NA  NA  NA   5  NA   4  NA  NA  NA
## item178  4  4  3 NA  3  4  2  4  1  NA   5   5   4   3   4  NA   4   3   4  NA
## item179  4  3  3  2 NA NA  4  4  5  NA  NA  NA  NA  NA  NA  NA   4  NA  NA  NA
## item180  3  3 NA  3 NA NA NA NA  4  NA  NA  NA   3  NA   5  NA   5  NA  NA   4
## item181  4  4  3  4  5  5  1  4 NA  NA   4   4   3   5  NA   3   4   3  NA  NA
## item182  4 NA NA  4 NA NA NA NA NA   3  NA  NA  NA  NA   4  NA  NA  NA  NA  NA
## item183  3  2 NA NA NA NA NA NA  3   1  NA  NA   5  NA   2  NA   4  NA  NA   1
## item184  3 NA NA NA NA NA NA NA NA  NA  NA  NA  NA  NA   5  NA   2  NA  NA  NA
## item185  4 NA NA NA NA NA NA NA  4  NA  NA  NA  NA  NA   5  NA   4  NA  NA  NA
## item186 NA  2  4  4  3  5 NA  4  2  NA   4   4   3  NA  NA   4   4   2  NA   5
## item187  4  4  4  2  5  4 NA  4  4  NA   5   5  NA  NA   4  NA   5   2  NA  NA
## item188  4  5  3  2  3  3  4  4  3  NA  NA   4  NA  NA  NA   4   5   4   5   5
## item189  2  4  3  4  5  4  4  4  4  NA   5   4   3   5   4   4   5   4   5   4
## item190  3  5  4  3  5  3 NA  4  2  NA   3   5  NA   4  NA   4   5   4   3   5
## item191  3  4  4  4  5  4 NA  4  3   4   5   5  NA   5  NA   4   5   4   5   5
## item192  5  5  4  2  5  4  2  4  2   4   5   5   5   5   5   4   4   4   5   5
## item193  4  4  4  2  5 NA NA  4  2  NA   4   5  NA  NA   4   4   4   3  NA  NA
## item194  4  4  4  4  5  5  3  5  5  NA   5   5   4   3  NA   5   5   4   4  NA
## item195  3  4  3 NA  5 NA NA  5  5  NA  NA   5  NA  NA  NA   5   4   4  NA  NA
## item196  4  5  2  4  3 NA  1  4  5  NA   5   5  NA  NA  NA   3   5   2   5  NA
## item197  4  5  3 NA  3 NA NA NA  4  NA  NA   4   5  NA  NA   5   5   3   5   5
## item198  2  4  3  5  5 NA NA  5  2  NA  NA   3  NA  NA  NA   4   4   3  NA  NA
## item199  4  4  3  1  3 NA NA  3  5  NA  NA   4   4  NA  NA   3   4   2  NA   5
## item200  4  4  3 NA NA NA NA NA NA  NA  NA  NA   3  NA  NA   3   2  NA  NA  NA
## item201  4  4  4  3  5 NA NA  5 NA  NA  NA   4  NA  NA  NA   5   2   2  NA  NA
## item202 NA  3  4  4  5  4 NA  5 NA  NA  NA   5  NA  NA  NA   3   5   2  NA  NA
##         V21 V22 V23 V24 V25 V26 V27 V28 V29 V30 V31 V32 V33 V34 V35 V36 V37 V38
## item118   4   5   4   4   5   4   5   3   5   4   4   4   3   4   5   5   5   5
## item119   4   5   5  NA   5   3   5  NA   5   3   3   4   4   3  NA   4   5   4
## item120   4   5   4   4   5   3   4  NA   5   4   2   4   4   3  NA   3   5   4
## item121   4   5   5   4   5   4   5   5   5   5   5   4   5   4   4   3   5   5
## item122   2   5   3   2  NA   3   4   5   5   5   5   2   4   4   4   3   2   4
## item123   3   5   3   3  NA   3   5   4   5   3   2   4   5   4   5   4   3   2
## item124   4   5   3  NA   5   2   1   4   5   2   3   4   3   4   5   4   2   4
## item125   3   5   5   4  NA   4   1   4   5  NA   1   4   1   1  NA  NA   2   4
## item126   3   5   5  NA   5   4   4   4   5   4   5   4   4   4  NA   3   3   4
## item127   4   5   5   2   5   4   3   5   5   2   5   4   4   4   5   3   2   4
## item128   1  NA   3   1  NA  NA   1   4  NA  NA  NA  NA  NA  NA  NA   2  NA   2
## item129  NA  NA   1  NA  NA  NA  NA  NA  NA   4  NA  NA   2  NA  NA  NA   2   4
## item130  NA  NA  NA  NA  NA  NA  NA  NA   2  NA  NA  NA  NA  NA  NA  NA  NA  NA
## item131   4  NA   4   3  NA   3   3   4   4   4   3   4   1   4   4   3  NA   4
## item132   2  NA  NA   2  NA  NA  NA  NA  NA  NA  NA  NA   5  NA  NA  NA  NA   2
## item133   2  NA  NA  NA  NA  NA  NA  NA   5   3  NA  NA   4  NA  NA  NA  NA   2
## item134   4  NA  NA  NA  NA  NA  NA  NA   2  NA  NA  NA   4  NA  NA  NA  NA   4
## item135   4   5   3   2   3   3   2   4   5   4   3   2   2   4   3   4   2   3
## item136   1  NA   4   1  NA   3   1  NA   3  NA  NA  NA   3  NA  NA   3  NA   1
## item137   3  NA   3   4  NA   4   2   5   4   4  NA  NA   5  NA  NA   3  NA   1
## item138   3  NA  NA   4  NA  NA  NA  NA   2  NA  NA  NA   4  NA  NA   3  NA   2
## item139  NA  NA  NA   4  NA  NA  NA   5  NA  NA  NA  NA   5  NA  NA  NA  NA   2
## item140   3   5   4   4  NA   4   2   5   4   4  NA   4   4   4   3   3  NA  NA
## item141   2   5   2   5   2   4   3   5   4   3   4   4   3   4   1   3   2   3
## item142   4   5   2   2   3   3   3   5   5   3  NA  NA   4  NA  NA   3   2   3
## item143   4  NA   4   4  NA   3   4   4   5   4  NA   4   5   2  NA   3  NA   3
## item144   2  NA   1   2  NA  NA  NA   4   3   4  NA  NA   5  NA  NA   3   1   4
## item146   1  NA  NA   1  NA  NA   1  NA   4  NA  NA  NA  NA  NA  NA   3  NA   2
## item147   4  NA  NA   5  NA  NA  NA  NA   5  NA  NA   2   3  NA  NA   3  NA  NA
## item148   4  NA  NA  NA  NA  NA  NA  NA   5  NA  NA  NA  NA  NA  NA   3  NA  NA
## item149   5   5   4   5   5  NA   4   4   5   4  NA   4   5   5  NA   4   5   2
## item150   4   5   4   2   5  NA   4   3   5  NA   3   4   5   4  NA   4   5   5
## item151   4   5   4   5  NA   3   4  NA   5   4   3   4  NA   3   5   3   4   4
## item152   1  NA   3   4   3  NA   3  NA   1   4  NA  NA  NA  NA  NA   3   1   4
## item153   4   5   5   4   3   4   5  NA   4  NA   5   5   3   5   4   3   3   5
## item154   4   5   5   3   5   3   4  NA   5   5   4   4   5   5   5   3   4   5
## item155   3   5   4   4   3  NA   2   2   2   3  NA   4   4   3  NA   4   2   5
## item156   4   5   5  NA   3  NA   2  NA   4  NA  NA  NA   3   4  NA   3   2   5
## item157   3   5   1  NA   5   3  NA  NA  NA   5   4   4   2   4   5   3   4   4
## item158   4   5   5   4  NA  NA   4   3   4  NA   3   4  NA   4  NA   5   5   4
## item159   5  NA  NA   5  NA  NA   2   4   5   5  NA  NA   5   3   4   5   3   4
## item160   4   5   5  NA   3   4   5   2   4   4   4   5   4   4   4   3   3   4
## item161  NA  NA  NA  NA  NA  NA  NA  NA  NA   3  NA  NA  NA  NA   4  NA  NA  NA
## item162   3   5   4   2  NA  NA   4  NA   5   4  NA  NA   2   3   4   3   3   4
## item163   4   5   5   5   5  NA   5   4   5   4  NA   4   4   3   5   4   3   4
## item164   3   5   4   2  NA  NA   5  NA   4   4  NA   4   3   3  NA   3   3   4
## item165   3  NA   4   5  NA  NA  NA  NA   5  NA  NA   4   2   4  NA   4  NA   5
## item166   4  NA   2   4  NA  NA  NA  NA   4  NA  NA   5   4   4   4   4  NA   5
## item167   4   5   5  NA  NA  NA   5  NA   4   3   3   4   3   4   5   4   4   4
## item168   4   5   4  NA   5  NA   5  NA   4  NA  NA   5   5   4  NA  NA   3   5
## item169   4  NA   5   5  NA  NA   4  NA   5   4   3   4  NA   4  NA   4   5   5
## item170   4   5   5   4   5   4   5  NA   5   4   3   4   4   5  NA   4   4   4
## item171   5   5   5   4  NA   3   5  NA   5   4   3   4   4   5  NA   4   5   5
## item172   4   5   5  NA   5   4   4  NA   5   5   3   4   5   5   5   4   4   5
## item173   3  NA   5  NA  NA   4   5  NA   4   3   5   4   3   3   5   4   3   5
## item174   4  NA   1  NA   4   4   4  NA   4  NA   3   4   4   3  NA   3   3   4
## item175   3  NA   1  NA   5   3  NA  NA   3  NA  NA   4   4   3  NA  NA  NA   5
## item176   4   5   4   3   5   3   5  NA   4   5   3   4   4   4   5   4   5   4
## item177   4  NA   1  NA  NA   3  NA   4   5  NA  NA   4  NA  NA  NA   3  NA  NA
## item178   4  NA   5   5   5   4   5  NA   4   4   3  NA  NA   4   5   4   2   5
## item179   4   5   5  NA  NA   4  NA  NA   4  NA  NA   4   4   4  NA  NA  NA   5
## item180   4  NA   4   5  NA   3  NA   4   5   4  NA   2   5  NA  NA   3  NA   3
## item181   4  NA   5   4   5   3   5  NA   3  NA   5   5   3   4   4   4   3   5
## item182  NA  NA  NA  NA  NA  NA  NA   4  NA   4  NA  NA   4  NA  NA  NA  NA  NA
## item183   1  NA  NA   4  NA  NA  NA   4   4   4  NA  NA   5  NA  NA   2   2   3
## item184   4  NA   1   5  NA  NA  NA  NA  NA  NA  NA   4   3   4  NA   3  NA   4
## item185  NA  NA  NA  NA  NA  NA  NA   4  NA  NA  NA   4  NA   1  NA   3  NA  NA
## item186   5  NA  NA   3  NA  NA   3  NA   4  NA  NA  NA   4   3  NA   4  NA   5
## item187   4  NA   4  NA   5   4   4  NA   2  NA  NA   4   4   3   5   4   4   5
## item188   4  NA   3   4  NA   4   5  NA   5  NA  NA   4  NA   4  NA   4   4   4
## item189   4   5   5   2   3   4   5   3   5   4   4   4   5   3  NA   4   4   5
## item190   4   5   5   4   5  NA   5  NA   5  NA   4   4   5   3  NA   4   4   4
## item191   4   4   5   3   5   3   5  NA   5  NA   3   4   5   3  NA   4   4   5
## item192   4   5   5   3   5   3   5   4   4  NA   3   4   5   2  NA   4   4   5
## item193   4  NA   3  NA   5  NA   4  NA   3  NA  NA   4   4   4  NA   3   4   4
## item194   4  NA   5   4   5   3   4  NA   4   4  NA   4   5   4   5   4   4   4
## item195   4  NA   1  NA  NA  NA  NA  NA  NA   4  NA   4  NA  NA  NA  NA   3   4
## item196   4  NA   5  NA   3   3   5  NA  NA  NA   3   4   3  NA   4   3   2   4
## item197   5  NA   2   4  NA  NA  NA  NA   4   4  NA  NA  NA  NA  NA   4   3   3
## item198   4  NA   4   3  NA  NA   4  NA   2  NA  NA   4   4  NA  NA   4   4   4
## item199   4  NA   4  NA  NA  NA   5  NA  NA   4  NA   4   4  NA  NA   3   5   5
## item200   4  NA   1  NA  NA  NA   5  NA  NA  NA  NA  NA  NA  NA  NA  NA   3   2
## item201   4  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   5  NA  NA  NA  NA   3   3
## item202   4  NA   4  NA   5  NA   3  NA  NA  NA  NA   4   5   4   5   5   5   4
##         V39 V40 V41 V42 V43 V44 V45 V46 V47 V48 V49 V50 V51 V52 V53 V54 V55 V56
## item118   5   4   4   3   5   4   4   4   4   5   2   3   5   4   4   4   4   2
## item119   4   4   4   3   5   4   4   2   4  NA   2  NA   5  NA   4   4   3   4
## item120   4   4   4   4   5   5   5   2   2   5   2  NA   4   5   3   4   4   5
## item121   5   5   3   4   5   2   5   5   4   5   2   3   4   5   2   5   3   5
## item122   3   3   2   2   3   4   4   5   5  NA   3   2   3   4  NA  NA   3   5
## item123  NA   5   5   2   5  NA   2   4   4   4   2   3   5   5  NA  NA   3   4
## item124   2   4   1   4   5   5   2   4   4   4   3   3   5   5   2   5   3   4
## item125   2  NA  NA   2   5   3   3   2   5   5   5  NA   3   5   1   5   2   4
## item126   5   5  NA   3   3   4   4   4   4   1   4   4   5   5   1   2   3   5
## item127   5   4   4   3   1   2   3   4   5   1   4   3   5   5  NA   4   4   4
## item128  NA  NA  NA   3  NA  NA  NA  NA   5  NA   4  NA  NA  NA   1  NA   2   1
## item129  NA  NA   3  NA  NA   5  NA  NA   4  NA   3  NA   3  NA  NA  NA  NA  NA
## item130  NA  NA  NA  NA  NA   1  NA  NA   4  NA   4  NA  NA  NA  NA  NA  NA  NA
## item131  NA   3   5  NA   5  NA   5   5   4  NA   4   3  NA   5   1  NA   2   5
## item132   3  NA  NA  NA   1  NA  NA  NA   4  NA   3  NA  NA   3  NA   3  NA  NA
## item133  NA  NA   1  NA  NA   4  NA   4   4  NA   3  NA  NA   3  NA  NA  NA   1
## item134  NA  NA  NA  NA  NA  NA  NA   1  NA  NA   5  NA  NA  NA  NA  NA  NA   4
## item135   5   3   3   5   2   4   4   5   4   2   3   4   4   5   3   4   4   5
## item136  NA  NA   2  NA  NA  NA  NA   1   2  NA   4  NA  NA  NA  NA  NA  NA  NA
## item137   3  NA   2  NA  NA  NA  NA  NA   5  NA   5   2  NA  NA   3  NA  NA   4
## item138  NA  NA  NA  NA  NA  NA  NA  NA   4  NA   5  NA  NA  NA  NA  NA  NA  NA
## item139   1  NA   2  NA  NA  NA  NA  NA   5  NA   3  NA  NA  NA   2  NA  NA   4
## item140   3   5   2  NA  NA   4   5  NA   4   1   2  NA  NA  NA  NA   3  NA   4
## item141   3   3  NA  NA   5   4   3   5   4   2   4   3   3   4   3   3   3   5
## item142   3  NA   3  NA  NA   3  NA   4   5   4   4   3  NA   3   2   3  NA   5
## item143   3   4   4  NA  NA   4   2  NA   4   5   3  NA  NA   5  NA   3   1   4
## item144  NA  NA   4  NA  NA   2  NA   4   5  NA   3  NA  NA  NA   2  NA   1   4
## item146  NA  NA  NA  NA  NA  NA  NA  NA   4  NA   3  NA  NA  NA  NA  NA  NA   1
## item147  NA  NA   5  NA  NA   2  NA  NA  NA  NA   4  NA  NA  NA  NA  NA  NA  NA
## item148  NA  NA  NA  NA  NA   3  NA  NA  NA  NA   5  NA  NA  NA  NA  NA  NA  NA
## item149   5   4   4   3  NA   4   5   5   5  NA  NA   4   4   5   3   4  NA   5
## item150   5   5   5   3   5  NA   5   2   4   5   3  NA   4   5   2   4   2   5
## item151   5   4   5   3   5   5   5   4   5  NA   5   4   4   4   2   4   2   4
## item152   4   5   1   4  NA   2   2   2   5  NA   5   4   4   4   2  NA   1   4
## item153   3   5   5   4   5  NA   5   4   3   4   3   4   3  NA   3   3   5  NA
## item154   5   4  NA   5   5   4   5   4   5   3  NA   4   3   5   4   5  NA   4
## item155   4   4   4   2  NA   1   3   2   5  NA  NA   4   4   4   3   3  NA   4
## item156   3   5  NA  NA   4  NA   4   4  NA  NA   3   4   3   5   2   5   4   4
## item157   5   5  NA   2  NA  NA   4   5  NA   4   3  NA   3   5   4   5   3   5
## item158   5   5   3   5   5   4   4   1   4   4   3  NA   4   5   2   5  NA  NA
## item159   3   3   4   3   1   2   4   1   4  NA   4   4   3   5   1  NA  NA   5
## item160   5   4   5   4   5   5   5   2   4  NA   3   4   3   5   3   3   4   3
## item161  NA  NA  NA  NA  NA   2  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA
## item162  NA   3  NA   4   2   5   5   1   4   1   3  NA   3   5   3   5   2   4
## item163   5   4  NA   2   5   5   5   4   4   4   3   4   3   5   2   5   4   4
## item164   5   4  NA   5   3   5   5   2   4   4   3  NA  NA   5   1   5   4   4
## item165  NA  NA  NA   2   1   4  NA  NA   4   3   3  NA  NA   5   5  NA   2   4
## item166  NA   4  NA   5   1  NA   5  NA   4   3   2  NA  NA   5  NA   4  NA   4
## item167  NA   5  NA   2   5   2   5   5   3   3   4   3   3   5  NA   5   3   4
## item168   5   5  NA   4   5   2   5   5   4   5   5  NA   4   5   2   5   2   4
## item169   5   5  NA   2   5  NA   5   4   5  NA   3  NA   5   5   2   5  NA   5
## item170   5   5   5   5   5   2   4   5   4  NA   3  NA   4   5   4   4  NA   5
## item171   5   5   3   2   4   4   5   5   5   5   4  NA   4   5   5   5   4   5
## item172   5   5  NA   4   5   4   5   5   5   5   4   4   4   5   4   5  NA   5
## item173   5   3  NA   4   2   3   5   1   3   5   4   4   3   5   2   5   4   5
## item174  NA   4  NA   4   5   1   5   1   4   4   5  NA   2   5   2   3  NA   4
## item175   5   5  NA  NA   5  NA   5   4   4   5   4   3  NA  NA  NA  NA   5   5
## item176   5   4   4  NA   5   1   5   4   4   5   4   4   5   5   2   5   5   4
## item177  NA  NA   4  NA   5  NA  NA  NA   3  NA   3  NA  NA  NA  NA  NA   2  NA
## item178   5   4   4  NA   5   3   5   2  NA  NA  NA   4   4   5   3   5   5   4
## item179  NA   5   5  NA  NA  NA  NA  NA   3  NA  NA  NA  NA   4   2  NA  NA   5
## item180  NA  NA   5  NA  NA   3  NA  NA   5   5  NA  NA  NA  NA   1  NA  NA   4
## item181   4   5  NA   2   5   3   4   5   5   5   3   4   3   4   1   5   5   5
## item182  NA  NA  NA  NA  NA   4  NA  NA   2  NA   3  NA  NA  NA  NA  NA  NA  NA
## item183   3  NA   5  NA  NA   4  NA  NA   5  NA   3  NA  NA  NA   2  NA  NA   4
## item184  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   4  NA  NA  NA  NA  NA  NA  NA
## item185  NA  NA  NA  NA  NA   4  NA  NA   4  NA   3  NA  NA  NA  NA  NA  NA  NA
## item186   5   5   4  NA   5   2  NA   2   5  NA   4  NA  NA  NA  NA  NA  NA   4
## item187   5   4   5  NA   4  NA  NA   2   5  NA  NA  NA   4  NA   1   4  NA   4
## item188  NA   4   5   5   5   5   5   2   4  NA  NA   4   4  NA  NA   5  NA   5
## item189   5   4   4   3   3   5   5   4   4   4   4   4   4   5   2   5  NA   5
## item190   5   5   5   4   3   1   5   4   5  NA   4   4   4   5   4   5   4   5
## item191   5   5   5   2   5  NA   5   5   4   5   4   4   4   5   2   5   4   5
## item192   5   5   5   5   5   3   5   5   4   5   4  NA   4   5   1   5   4   5
## item193   5   5  NA   2   2  NA   5   2   4   5   3   3   4   5   3   5   3   4
## item194   5   4   4   4   4  NA  NA   4   4  NA   3   4   4   5   2   5   3   4
## item195   4   4  NA   4  NA  NA   5   1   4  NA   4  NA   4  NA   2   4  NA  NA
## item196   4   4  NA  NA   5   4   5   2   3  NA   4   4   3   5   5   4   4   4
## item197   5  NA   5  NA   5   5   3   4   5  NA   4   4   4  NA   1  NA  NA   4
## item198  NA  NA  NA  NA   5   4   5   1   4  NA   3  NA  NA   5  NA   5  NA   4
## item199   5  NA   5   2   2   2   5   4   5  NA  NA   4   4  NA   1   5  NA   4
## item200  NA  NA   3  NA   5  NA  NA   5   4  NA  NA  NA  NA  NA  NA  NA  NA  NA
## item201  NA  NA  NA   3  NA  NA  NA  NA   3  NA  NA  NA  NA  NA  NA   5   3  NA
## item202   5   4  NA   5   1  NA  NA  NA   4  NA  NA  NA  NA  NA   2   4  NA   5
##         V57 V58 V59 V60 V61 V62 V63 V64 V65 V66 V67 V68 V69 V70 V71 V72 V73 V74
## item118   3   4   5   5   4   4   5   5   5   5   3   3   2   3   2   4   2   5
## item119  NA   4   4   4   4   4  NA   4  NA  NA   5   4   4   3   1   3   5   5
## item120  NA   4   3   3   4   3  NA   3  NA  NA   5   2   4   4   1   4   5   4
